---
title: "TB Trends Analysis"
author: "Your Name"
date: "2024-03-15"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load necessary libraries

```{r}
library(pacman)
library(tidyverse)
library(tbmod)
library(ggplot2)
library(cowplot)
library(patchwork)
theme_set(theme_minimal_grid() + panel_border(color = "black"))
```

# Check the version of the 'tbmod' package

```{r}
packageVersion("tbmod")
```

# Set paths for input and output files

```{r}
paths <- set.paths(
  countries = "countries",
  countrycode = "IND",
  xml = "test_undernutrition_mixing_2021.xml"
)
```

# Run the 'tbmod' model

```{r}
output <- run(paths, sample.parameters = FALSE, output.flows = FALSE, write.to.file = TRUE)
```

# Extract TB trends data from the output

```{r}
TB_trends <- output$stocks
```

# Filter out rows where the values in the "TB" column contain the substring "count"

```{r}
TB_trends_filtered <- TB_trends %>%
  filter(!str_detect(TB, "count"))
```

# Summarize the filtered data by TB compartment and year

```{r}
sum_by_TB <- TB_trends_filtered %>%
  group_by(TB,year,RISK) %>%
  summarize(total_value = sum(value))
```

# Create a line plot showing population in each TB compartment over time

```{r}
ggplot(sum_by_TB, aes(x = year, y = total_value, color = TB)) +
  geom_line() +
  labs(x = "Time", y = "Population in Compartment", color = "tbmod compartment") +
  theme_minimal() +
  facet_wrap(~RISK,)
```

# Summarize TB values by year

```{r}
pops <- sum_by_TB %>%
  group_by(year,RISK) %>%
  summarise(population = sum(total_value))
```

```{r}
sum_tb_values <- TB_trends %>%
  filter(TB %in% c("Ds", "Dc")) %>%
  group_by(year,RISK) %>%
  summarise(prevalence_value = sum(value))
```

```{r}
sum_tb_values <- left_join(sum_tb_values, pops, by = c("year","RISK"))
```

```{r}
sum_tb_values <- sum_tb_values %>%
  mutate(prev_per_100000 = (prevalence_value / population) * 100000)
```

```{r}
ggplot(sum_tb_values, aes(x = year, y = prev_per_100000)) +
  geom_line() +
  labs(x = "Time", y = "Prevalence per 100,000") +
  theme_gray() +
  scale_y_continuous(limits = c(0, max(sum_tb_values$prev_per_100000))) +
  facet_wrap(~RISK, scales = "free_y")
```

# Create a line plot showing Population over time

```{r}
ggplot(sum_tb_values, aes(x = year, y = population, color = RISK)) +
  geom_line() +
  labs(x = "Time", y = "Population") +
  # theme_gray() +
  scale_y_continuous(limits = c(0, max(sum_tb_values$population)))
```

```{r}
# Group by year
grouped_df <- group_by(sum_tb_values, year)

# Calculate RR for each year
RR_by_year <- summarise(grouped_df,
                        RR_mild = mean(prev_per_100000[RISK == "mild"]) / mean(prev_per_100000[RISK == "normal"]),
                        RR_moderate = mean(prev_per_100000[RISK == "moderate"]) / mean(prev_per_100000[RISK == "normal"]),
                        RR_over = mean(prev_per_100000[RISK == "over"]) / mean(prev_per_100000[RISK == "normal"])
)

# Reshape data from wide to long format
RR_long <- tidyr::pivot_longer(RR_by_year, cols = starts_with("RR"), names_to = "Risk_Level", values_to = "Relative_Risk")

# Plot
ggplot(RR_long, aes(x = year, y = Relative_Risk, color = Risk_Level)) +
  geom_line() +
  labs(title = "Relative Risk of Infectious Tuberculosis by Year",
       x = "Year",
       y = "Relative Risk") 
  # theme_minimal()

```

```{r}

sum_tb_values_CNR <- TB_trends %>%
  filter(TB %in% c("Rt")) %>%
  group_by(year,RISK) %>%
  summarise(prevalence_value = sum(value))


```

```{r}
sum_tb_values_CNR <- left_join(sum_tb_values_CNR, pops, by = c("year","RISK"))
```

```{r}
sum_tb_values_CNR <- sum_tb_values_CNR %>%
  mutate(prev_per_100000 = (prevalence_value / population) * 100000)
```

```{r}
ggplot(sum_tb_values_CNR, aes(x = year, y = prev_per_100000)) +
  geom_line() +
  labs(x = "Time", y = "Case Notification Rate per 100,000") +
  theme_gray() +
  scale_y_continuous(limits = c(0, max(sum_tb_values_CNR$prev_per_100000))) +
  facet_wrap(~RISK, scales = "free_y")
```

í

```{r}

sum_tb_values_burden <- TB_trends %>%
  filter(TB %in% c("Ds","Dc","Dm")) %>%
  group_by(year,RISK,TB) %>%
  summarise(prevalence_value = sum(value))


```

```{r}
sum_tb_values_burden <- left_join(sum_tb_values_burden, pops, by = c("year","RISK"))
```

```{r}
sum_tb_values_burden <- sum_tb_values_burden %>%
  mutate(prev_per_100000 = (prevalence_value / population) * 100000)

sum_tb_values_burden$year <-  as.integer(sum_tb_values_burden$year)
```

```{r}
p1 <- ggplot(sum_tb_values_burden, aes(x = year, y = prev_per_100000, color = TB)) +
  geom_line() +
  labs(x = "Time", y = "Case Notification Rate per 100,000") +
  theme_gray() +
  scale_y_continuous(limits = c(0, max(sum_tb_values_burden$prev_per_100000))) +
  facet_wrap(~RISK, scales = "free_y")
p1
```

```{r}
datafrom_plot <- ggplot_build(p1)$data
```

```{r}
filtered_data <- sum_tb_values_burden[sum_tb_values_burden$year == 2024, ]
str(filtered_data)
```

```{r}
ratio_df <- filtered_data %>%
  group_by(RISK) %>%
  summarize(Ds_Dc_ratio = prevalence_value[TB == "Ds"] / prevalence_value[TB == "Dc"],
            Dm_Dc_ratio = prevalence_value[TB == "Dm"] / prevalence_value[TB == "Dc"])

clipr::write_clip(ratio_df)
ratio_df
```

\
